---
title: "AAPI Data Ethnic Group Profile"
params:
  group: "test"
output:
  html_document:
    theme: simplex
    toc: TRUE
    
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(DT)
library(readxl)
library(tidyverse)
library(highcharter)

main_data <- read_excel('~/ethnic_group_profiles/maindata.xlsx')
group_selected <- main_data %>% filter(ethnic_group == params$group)


current_group <- group_selected$ethnic_group[1]
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(round(x,2), big.mark=",", digits=6) } })
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- ","
options(highcharter.lang = hcoptslang)
```

## Who are <span class="output_style">`r current_group` Americans?</span>


There are <span class="output_style">`r group_selected$asian_alone_pop` `r current_group` Americans</span> in the United States, which represents about <span class="output_style">`r group_selected$pct_asian_alone`%</span> percent of the total Asian Alone population. 



```{r, echo=FALSE, message=FALSE, warning=FALSE}

main_data<- main_data %>% arrange(asian_alone_pop)
all_butselected<- main_data %>% filter(ethnic_group != current_group)
# hchart(main_data, "bar", hcaes(x = ethnic_group, y = asian_alone_pop)) %>%
# hc_rm_series(names = "Vietnamese") %>%
# hc_add_series_labels_values(group_selected$ethnic_group, group_selected$asian_alone_pop,type = "bar")%>% 
#   hc_yAxis(title = list(text = "Population")) %>%
#   hc_xAxis(title = list(text = "Ethnic Group")) %>%
#   hc_add_theme(hc_theme_flat()) 



hchart(all_butselected, "bar", hcaes(x = ethnic_group, y = asian_alone_pop)) %>%
hc_add_theme(hc_theme_flatdark()) %>%
hc_add_series_labels_values(group_selected$ethnic_group, group_selected$asian_alone_pop,type = "bar")%>% 
  hc_yAxis(title = list(text = "Population"),
         labels= list(style =list(color ="#fff", fontSize='12px'))) %>%
  hc_xAxis(title = list(text = "Ethnic Group"),
           labels= list(style =list(color ="#fff", fontSize='15px'))) %>%
 hc_title(text = "Asian American By Detailed Origin",
           margin = 20, align = "left",
           style = list(color = "#E26069"))%>%
  hc_subtitle(text = "(2011-2015 ACS)",
            margin = 20, align = "left",
           style = list(color = "#E26069")) %>%
  hc_chart(backgroundColor ='#262324')
```



## Educational Attainment

According to the latest data from the <span class="output_style">`r group_selected$data_source`</span>, <span class="output_style">`r group_selected$pct_hsdegree_higher`% of `r current_group` Americans </span>have at least a High School Diploma or GED which is <span class="output_style">`r group_selected$pct_diff_with_total_hshiggher``r group_selected$higher_lower`</span> than Asian Americans a whole.

In terms of higher education, <span class="output_style">`r group_selected$pct_ba_higher`% of `r current_group` Americans </span> hold at least a Bachelor's Degree or higher compared to <span class="output_style">`r group_selected$asian_total_pct_ba_higher`%</span> of Asian Americans as a whole.


## Limited English Proficiency

An important feature of Asian American and Pacific Islander, or AAPI, communities
is their language diversity and variations in their levels of English proficiency across
groups. English proficiency is important because it is significantly related to outcomes
such as earnings, occupational mobility, quality of health care, and the ability to participate
in civic and political life. There are <span class="output_style">`r group_selected$asian_total_lep`</span> Asian Americans in the U.S. who are limited english proficient (LEP).

Among <span class="output_style">`r current_group` Americans</span>, <span class="output_style">`r group_selected$asian_pct_lep`%</span> (or <span class="output_style">`r group_selected$total_lep`</span>) are limited english proficient, compared to <span class="output_style">  `r group_selected$asian_pct_lep`%</span> for Asian Americans as a whole.






